### 2018-04-22 papers/synth/intro.tex
intro

% Describe VTS in detail
While molecules are transported by VTSs, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active along in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
compartment.
%
Not all the pairs of molecules can participate in the fusion, it is
usually determined by wet experiments the potential fusion pairs.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
Since a molecule has to be active in order to participate in fusion,
the molecule may be present in the other places without being active
and does not interfere with regulation of the other fused
channel-compartment pairs.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation {\em activity functions}.

Although the VTSs are very important, our understanding

In the VTS model, we assume that the system is in study state and
the concentration of molecules does not change over time.
%
Therefore, there is no aspect of

%
They are known

Some of the molecules that are pre
%
%
Different compartments are viewed as nodes and transport channels are
nodes between the graphs.

\ashu{Make a case for incomplete knowledge of VTSs.}
%Now we will work on
Since VTSs are partially known, 
%
the labels may not have been fully observed.

@@

We model a VTS as a labelled graph.
%
Each compartment of VTS is a node of the graph and and the
transport channels between the nodes is an edge.
%
The set of molecules present in a compartment is the label of
the compartment.
% 
Similarly, the set of transported molecules carried by an edge is the label
on the edge.
%
A molecule in a node or edge may be active or inactive. 
%
The constraints discussed on the VTSs that allow a VTS to be feasible
are combinatorial in nature, for example stability or 3-connectedness.
%
The problem of synthesizing parts of a VTS that are unobserved such that 
the modified VTS

>>>>

% Describe VTS in detail
While molecules are transported by VTSs, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active along in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
compartment.
%
Not all the pairs of molecules can participate in the fusion, it is
usually determined by wet experiments the potential fusion pairs.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
Since a molecule has to be active in order to participate in fusion,
the molecule may be present in the other places without being active
and does not interfere with regulation of the other fused
channel-compartment pairs.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation as {\em activity functions}.

% Defending our model
%
In the VTS model, we assume that the system is in study state and
the concentrations of the molecules do not change over time.
%
Therefore, the system only has aspects of a network or a graph.
%
We model the system as a labelled graph, where compartments are nodes and
transport channels are edges.
%
The set of molecules present and their activity in a compartment or
a channel is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing matrix
containing Boolean values for each pair of molecules and activity
Boolean functions.
%
Since the system is in study state, we expect that any molecule that
leaves a compartment must come back via some path on the graph.
%
We call this property of VTS as {\em stability}.

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means patch work of wet experiments~\cite{model} for
identifying the compartments, channels, molecules, their activity, and
regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system.
%
The search for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
For example, we suspect that some edges are missing from the graph, since
we expect the must satisfy stability.
%
Due the combinatorial nature of graphs, the search space is huge and often
hard to enumerate naively.
%
We need specialized methods to perform the search.

%
We may translate the problem into a synthesis question, in which 
we have a partial system  and a given property that
the system needs to satisfy.
%
The synthesis method completes the system such that the property
is satisfied by it.
%

In synthesis, we may have a partial

@@

The constraints discussed on the VTSs that allow a VTS to be feasible
are combinatorial in nature, for example stability or 3-connectedness.
%
The problem of synthesizing parts of a VTS that are unobserved such that 
the modified VTS
